Exploring the Determinants of Body Weight: A Bayesian Analysis of Anthropometric and Demographic Factors Among Female U.S. Army Personnel

### 2024-12-02 paper/paper.qmd
update paper, scripts, references

# Introduction {#sec-intro}

Body weight significantly influences physical performance, health, and operational readiness in demanding occupations like military service. In the U.S. Army, maintaining optimal weight is essential for meeting fitness standards, minimizing injury risks, and ensuring operational efficiency. Despite the availability of extensive anthropometric and demographic data, limited research examines how these factors collectively impact body weight, particularly among female soldiers [@gordon2014].

This study addresses this gap using the 2012 U.S. Army Anthropometric Survey (ANSUR II) Female Dataset, which includes rigorous anthropometric and demographic measurements of female personnel. Data collection employed standardized instruments, such as stadiometers and calipers, ensuring consistency and reliability [@hotzman2011; @paquette2009]. Variables like height, waist circumference, and thigh circumference were measured to capture body composition, while demographic data such as age, ethnicity, and military component were cross-verified with administrative records [@gordon2014].

The analysis highlights anthropometric variables as strong predictors of body weight and demographic factors as additional contributors. These findings support personalized fitness programs, improved health outcomes, and optimized military gear for enhancing operational readiness [@opendesignlab2018; @paquette2009].

This paper is organized as follows: Section [@sec-intro] provides an overview of the study's background and objectives. Section [@sec-data] introduces the dataset and offers an analysis of key variables. Section [@sec-model] details the methodology, including the Bayesian regression model employed. Section [@sec-result] presents the results, emphasizing the significance of predictors and model performance. Section [@sec-discussion] explores the study's limitations and provides directions for future research. Lastly, Section [@sec-model-details] presents posterior predictive checks, diagnostic plots, and their interpretations.

## Estimand

This study seeks to estimate the relationship between body weight and a set of key anthropometric and demographic variables among female U.S. Army personnel. Specifically, it aims to quantify how variations in anthropometric measurements, such as height and waist circumference, as well as demographic factors, including age and ethnicity, influence body weight. The objective is to identify significant predictors and develop a robust predictive model to enhance understanding and practical applications in health monitoring, fitness interventions, and equipment design.

@@

library(tidyverse)
library(tinytable)
library(dplyr)
library(arrow)
library(knitr)
library(ggplot2)

# Load the dataset
file_path <- "../data/analysis-data/ansur_female_data.csv" 
ansur_female <- read_csv(file_path)

```

@@

The dataset contains anthropometric and demographic measurements for 1,986 female U.S. Army personnel, collected by the Natick Soldier Research, Development, and Engineering Center (NSRDEC) using standardized protocols. Variables such as stature, waist circumference, and chest circumference were measured with precise instruments, while demographic data like age and military component were cross-verified with administrative records to ensure accuracy.

While other datasets related to anthropometric measurements are publicly available, they typically focus on civilian populations or mixed-gender samples and do not offer the level of specificity needed for military personnel. Access to military-specific datasets is often restricted due to security and privacy concerns, making the ANSUR II dataset one of the few comprehensive sources for this population. This scarcity highlights the unique value of the ANSUR II dataset for understanding the anthropometric and demographic characteristics of female U.S. Army personnel.

@@

The data for this study was systematically downloaded, cleaned, analyzed, modeled, and visualized using R [@citeR], an extensive statistical programming language. The following packages were used for this study:

- **`tidyverse`** [@tidyverse]: To streamline the process of data manipulation and visualization.
- **`ggplot2`** [@ggplot2]: Used for its powerful and flexible capabilities in creating various types of visualizations tailored to the needs of this study.
- **`dplyr`** [@dplyr]: Employed for its intuitive functions to transform and summarize complex datasets effectively.
- **`rstanarm`** [@rstanarm]: Facilitated the implementation of Bayesian models, providing a straightforward way to fit regression models using Stan.
- **`bayesplot`** [@bayesplot]: Utilized for creating graphical posterior predictive checks and diagnostic plots to assess model fit.
- **`arrow`** [@arrow]: Used for efficiently reading and writing large datasets, enhancing data handling capabilities.
- **`tinytable`** [@tinytable]: Used to create compact and well-organized summary tables for presenting data and model outputs effectively.
- **`modelsummary`** [@modelsummary]: Used for creating professional-quality regression tables and visualizations to summarize model results clearly.
- **`knitr`** [@knitr]: Employed to dynamically generate reproducible reports that integrate R code with its outputs, allowing for seamless inclusion of plots and analysis results in the final document.
- **`janitor`** [@janitor]: Used for its efficient data cleaning functions, simplifying the process of preprocessing dirty data into a clean, analysis-ready format.
- **_Telling Stories with Data_** [@tellingstories]: This book was consulted for its statistical information.

```{r}
#| label: tbl-head-data
#| tbl-cap: First 6 rows of the cleaned dataset
#| echo: false
#| warning: false
#| message: false

ansur_female |>
  head() |>
  kable(booktabs = TRUE, align = "c")
```

@@

### Body Weight in Pounds {#sec-body-weight}

@@

ggplot(data = ansur_female, aes(x = weightlbs)) +
  geom_histogram(binwidth = 2, fill = "steelblue", color = "grey50") +
  labs(
    x = "Body Weight (lbs)",
    y = "Count"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))

```

@@

### Height {#sec-height}

@@

ggplot(data = ansur_female, aes(x = heightin)) +
  geom_histogram(binwidth = 2, fill = "darkgreen", color = "grey50") +
  labs(
    x = "Height (inches)",
    y = "Count"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))

```

### Waist Circumference {#sec-waist-circumference}

@@

### Thigh Circumference {#sec-thigh-circumference}

@@

# Example dataset (use your cleaned data instead)
data <- ansur_female

@@

# Create violin plots
ggplot(data_long, aes(x = measurement, y = value, fill = measurement)) +
  geom_violin(trim = FALSE, alpha = 0.7) +  # Violin plot with full tails
  geom_jitter(width = 0.2, alpha = 0.5, color = "black") +  # Overlay actual data points
  theme_minimal() +
  labs(
    x = "Measurement",
    y = "Circumference (in cm)",
    fill = "Measurement"
  ) +
  theme(legend.position = "none")

```

### Age {#sec-age}

@@

# Summary statistics for age
age_summary <- ansur_female %>%
  summarise(
    Min = min(age, na.rm = TRUE),
    `1st Quartile` = quantile(age, 0.25, na.rm = TRUE),
    Median = median(age, na.rm = TRUE),
    `3rd Quartile` = quantile(age, 0.75, na.rm = TRUE),
    Max = max(age, na.rm = TRUE),
    Mean = mean(age, na.rm = TRUE),
    SD = sd(age, na.rm = TRUE)
  )

@@

# Display the table
age_table

```

### Component {#sec-component}

@@

# Frequency table for component
component_summary <- ansur_female %>%
  count(component) %>%
  mutate(Percentage = round(n / sum(n) * 100, 2))

@@

# Display the table
component_table

```

@@

The model’s design reflects the characteristics of the dataset to ensure alignment with the nature of the variables and optimize the analysis. Anthropometric variables such as height, waist circumference, and thigh circumference were included as continuous predictors to preserve their granularity and maximize sensitivity to subtle variations in body weight. Age was also treated as a continuous variable, rather than being grouped into categories, to avoid arbitrary cutoffs and retain variability, enabling a more precise assessment of its relationship with body weight. The military component variable was modeled categorically, with each group (Regular Army, Reserves, and National Guard) treated as a distinct level to account for structural differences in activity levels and lifestyle among these groups. Additionally, waist and thigh circumferences were rescaled to centimeters for consistency and to reflect standard real-world measurement practices. These decisions ensure that the model leverages the dataset’s structure effectively while maintaining interpretability and relevance to the research context.

@@

-   Intercept Priors: For the model’s intercept $\beta_0$, a normal prior distribution is used with a mean of 0 and a standard deviation of 1. This choice reflects the assumption that the baseline body weight (when all predictors are zero) is centered near the observed scale of the outcome variable but avoids imposing overly strong constraints. The standard deviation of 1 allows for reasonable variation, ensuring the prior does not dominate the posterior estimates. Given the scale of the predictors (e.g., height, waist circumference), this weakly informative prior stabilizes the intercept estimate without introducing bias.

@@

The weakly informative priors are designed to enhance the model’s robustness, ensuring credible parameter estimates and reliable uncertainty quantification. The use of Bayesian priors provides an added layer of rigor, particularly when estimating complex relationships between predictors and body weight. The rstanarm package facilitates the implementation of these priors, making Bayesian inference accessible and effective for this analysis.

@@

A frequentist linear regression model was also considered for its simplicity and interpretability; however, it does not provide posterior distributions or credible intervals, which are essential for quantifying uncertainty in this study. By contrast, the Bayesian regression framework provides probabilistic estimates, enabling uncertainty quantification and credible intervals for the coefficients. This approach aligns well with the study’s objectives, where understanding the relative influence of predictors on body weight requires a robust and interpretable model. The rstanarm package was chosen for its efficient handling of Bayesian inference and built-in diagnostics, ensuring rigorous validation. The Gaussian likelihood function complements the continuous nature of the outcome variable (body weight), and the model structure strikes a balance between simplicity and capturing key relationships in the data.

@@

The Bayesian regression model was developed to investigate the relationship between body weight and key anthropometric and demographic predictors among female U.S. Army personnel. The predictors included height, waist circumference, thigh circumference, age, and military component. The analysis identified significant positive associations between body weight and the anthropometric predictors—height, waist circumference, and thigh circumference—highlighting their strong influence on body weight. Age and military component demonstrated smaller but meaningful effects, reflecting their nuanced contributions to variations in body weight. A summary of these findings is presented in [@tbl-bayesian-model-summary].

@@

library(rstanarm)
ansur_bayesian_model <-
  readRDS(file = here::here("models/ansur_bayesian_model.rds"))

```

@@

# Create a summary table using modelsummary
modelsummary(
  list("Bayesian Regression Model" = ansur_bayesian_model),
  statistic = c("conf.int", "std.error"), # Include credible intervals and standard errors
  stars = FALSE,                         # Disable statistical significance stars
  gof_omit = ".*"
)

```

@@

The model’s intercept represents the baseline body weight when all predictors are at their reference levels or zero. While this value lacks direct interpretability due to the unrealistic scenario of zero predictors, it provides a conceptual starting point for the model. These findings emphasize the importance of anthropometric measurements in predicting body weight while underscoring the need for further exploration of demographic factors to refine the model.

@@

posterior <- as.matrix(ansur_bayesian_model)

mcmc_areas(
  posterior,
  pars = c("(Intercept)", "heightin", "waist_circumference", "thigh_circumference", "age", "componentArmy Reserve", "componentRegular Army"),
  prob = 0.89, # 89% credible intervals
  prob_outer = 0.95
) +
  ggtitle("Posterior Distributions of Coefficients") +
  xlab("Estimated Effect") +
  theme_classic()

```

@@

The Bayesian regression analysis underscores the significant positive associations between body weight and anthropometric predictors, particularly waist circumference and thigh circumference, among female U.S. Army personnel. These findings highlight the critical role of body composition measurements in explaining variations in body weight. Conversely, the uncertain effects of height, age, and military component suggest that these factors contribute less reliably to the model, reflecting the multifaceted nature of weight determinants. These results affirm the utility of anthropometric data in health monitoring and fitness interventions while identifying areas for further refinement. Exploring additional predictors may enhance the model’s explanatory power and improve its utility in practical applications.

@@

@@

Expanding the dataset’s scope to include longitudinal measurements would also enable researchers to explore dynamic relationships between body composition, fitness, and operational readiness. Such studies could inform policies for optimizing physical performance and reducing long-term health risks among service members.

This research underscores the utility of anthropometric measurements in predicting body weight, providing actionable insights for health monitoring, fitness interventions, and military equipment design. For instance, the findings could guide the development of tailored fitness programs to address central adiposity (waist circumference) and muscle mass (thigh circumference), enhancing operational readiness and reducing injury risks. These insights align with broader public health objectives, such as the World Health Organization’s emphasis on preventing obesity-related conditions through effective weight management strategies.

@@

The raw ANSUR II Female Dataset was systematically cleaned and prepared for analysis to ensure consistency, accuracy, and relevance of the variables. First, the raw dataset was loaded using the read_csv function and processed with the janitor::clean_names() function to standardize column names, making them easier to interpret and work with. Key variables relevant to the study—such as weight (weightlbs), height (heightin), waist circumference, thigh circumference, age, and military component—were selected using the select() function to focus the analysis on predictors of interest.

@@

[@fig-ppcheckandposteriorvsprior-1] presents a posterior predictive check to evaluate how well the model predicts the observed data. This diagnostic compares the simulated data from the model’s posterior distribution with the actual observed data, providing insights into the model's adequacy. A good fit is characterized by overlapping distributions of predicted and observed values, indicating that the model effectively captures key characteristics of the data.

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: Examining how the model fits, and is influenced by the data.
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

library(here)

file_path <- here::here("data", "analysis-data", "ansur_female_data.parquet")

# Check if the file exists before attempting to read
if (file.exists(file_path)) {
  sampled_ansur_data <- read_parquet(file_path) %>%
    sample_n(1000)  # Sample 1000 rows
} else {
  stop("File not found: ", file_path)
}
pp_check(ansur_bayesian_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(ansur_bayesian_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()

```

@@

[@fig-stanareyouokay-1] presents a trace plot, which assesses the convergence of the Markov Chain Monte Carlo (MCMC) algorithm by examining the sampled values for each parameter across iterations. The chains for each parameter exhibit good mixing, with no discernible trends or patterns over the iterations. The consistent overlap of chains indicates that the sampling algorithm has effectively explored the posterior distribution. These results suggest that the Bayesian model’s estimates are reliable and not overly sensitive to initial values or random sampling variation.

@@

plot(ansur_bayesian_model, "trace")

plot(ansur_bayesian_model, "rhat")

```

# Ideal Data Sampling Methodology

In an ideal scenario, the data for this study would be collected using a stratified random sampling method to ensure the sample accurately represents the diverse population of female U.S. Army personnel. This approach would involve dividing the population into distinct strata based on key demographic and occupational characteristics, such as military component (Active Duty, Reserves, National Guard), age groups (e.g., 18–25, 26–35, 36+ years), and ethnic backgrounds. Each stratum would then be sampled independently, with participants randomly selected within each group in proportion to their representation in the overall population. Stratified random sampling is particularly effective for heterogeneous populations, as it minimizes sampling bias and ensures that smaller subgroups, such as Reserve personnel or older age groups, are adequately represented.

To implement this method, a comprehensive roster of all female U.S. Army personnel would be required. This roster would include essential demographic and occupational information to accurately classify individuals into strata. Once stratification is complete, participants would be selected using randomization techniques, such as computer-generated random numbers, to eliminate selection bias. For instance, if 50% of the total population comprises Active Duty personnel, 50% of the sampled participants would also be drawn from this stratum. Similarly, if 20% of personnel fall within the 18–25 age group, this age group would constitute 20% of the sample. This proportional allocation ensures that the sample mirrors the characteristics of the entire population.

To account for potential response rate challenges, oversampling could be employed within underrepresented strata, such as ethnic minorities or Reserve personnel. If the expected response rate is 50%, twice the number of targeted participants would be recruited within these strata to ensure adequate representation. Such measures would enhance the reliability of results and reduce the margin of error.

To enhance the validity and reliability of the data, standardized measurement protocols would be employed during data collection. Anthropometric measurements, such as weight, height, waist circumference, and thigh circumference, would be conducted using calibrated instruments and performed by trained professionals to reduce variability. Demographic data, such as age, ethnicity, and military component, would be collected through self-reports and cross-verified with official administrative records to ensure accuracy and consistency.

@@

## Survey Recruitment and Administration

Respondents would be recruited using a multi-channel approach to ensure diverse participation. Recruitment channels could include:

-   Direct Military Channels: Leveraging internal communication systems within the U.S. Army, such as newsletters, email campaigns, or in-person events at military bases.

-   Online Platforms: Using targeted outreach through platforms like military spouse groups, service member forums, and Army-related social media networks.

-   Incentives for Participation: Offering small incentives, such as participation in gift card sweepstakes or recognition within the military community, to encourage response rates.

Surveys would be administered both online and in person, with the online version accessible through secure platforms like Google Forms or SurveyMonkey. For in-person administration, trained personnel would conduct the survey at military facilities, ensuring participants are guided through the questions.

@@

### Section 1: Demographic Information
1. **What is your age?** (Open-ended)  
   Example answer: 25

2. **Which military component are you currently serving in?** (Multiple-choice)  
   - Regular Army  
   - Army Reserve  
   - National Guard

3. **What is your ethnic background?** (Multiple-choice)  
   - White  
   - Black or African American  
   - Asian  
   - Hispanic or Latino  
   - Native American or Alaska Native  
   - Native Hawaiian or Pacific Islander  
   - Other (please specify): ___________

### Section 2: Anthropometric Measurements
*(Instructions: Please provide accurate measurements. Measurements should be taken by a trained professional or using calibrated equipment.)*

4. **What is your body weight in pounds?** (Open-ended)  
   Example answer: 142

5. **What is your height in inches?** (Open-ended)  
   Example answer: 64

6. **What is your waist circumference in centimeters?** (Open-ended)  
   Example answer: 85.0

7. **What is your thigh circumference in centimeters?** (Open-ended)  
   Example answer: 62.2

>>>>

# Introduction

Body weight plays a critical role in physical performance, health, and operational readiness, particularly in demanding professions such as military service. For the U.S. Army, maintaining optimal weight is crucial to meet fitness standards, reduce injury risks, and ensure operational efficiency. While extensive anthropometric and demographic data exist, limited research explores the combined influence of these factors on body weight, particularly among female soldiers [@gordon2014].

This study addresses this gap by leveraging the 2012 U.S. Army Anthropometric Survey (ANSUR II) Female Dataset, which includes precise anthropometric and demographic measurements of female personnel. Data collection utilized standardized instruments such as stadiometers and calipers, ensuring high reliability and consistency [@hotzman2011; @paquette2009]. Key variables, including height, waist circumference, and thigh circumference, were measured to assess body composition, while demographic factors such as age, ethnicity, and military component were cross-validated with administrative records [@gordon2014].

The primary aim of this study is to model the relationship between body weight and a set of anthropometric and demographic predictors among female U.S. Army personnel. Specifically, it quantifies how variations in measurements such as height and waist circumference, alongside demographic factors like age and ethnicity, contribute to body weight. The goal is to identify significant predictors and develop a robust predictive model that can inform health monitoring, tailored fitness programs, and ergonomic equipment design.

Preliminary findings underscore the strong predictive power of anthropometric variables in determining body weight, with demographic factors serving as additional contributors. These insights support the development of personalized fitness interventions, improved health outcomes, and the optimization of military gear to enhance operational readiness [@opendesignlab2018; @paquette2009].

This paper is structured as follows: [@sec-data] describes the dataset and provides a descriptive analysis of the key variables. [@sec-model] explains the methodology, including the Bayesian regression model employed. [@sec-result] presents the findings, highlighting significant predictors and model performance. [@sec-discussion] discusses the implications, limitations, and future research directions. Lastly, [@sec-model-details] offers detailed posterior predictive checks, diagnostic plots, and their interpretations.

@@

The ANSUR II dataset provides comprehensive anthropometric and demographic data for 1,986 female U.S [@ansurII_female]. Army personnel, collected using standardized protocols to ensure accuracy. Unlike civilian datasets, it uniquely addresses the physical demands and characteristics of military personnel, offering rare insights into factors like fitness, injury risk, and gear design [@hotzman2011]. Its specificity makes it a vital resource for understanding and improving the health, safety, and operational readiness of female soldiers [@paquette2009].

```{r}
#| echo: false
#| warning: false
#| message: false
library(tidyverse)
library(tinytable)
library(arrow)
library(knitr)

# Load the dataset
analysis_data <- read_parquet(here::here("data", "02-analysis_data", "analysis_data.parquet"))
```

@@

The dataset comprises anthropometric and demographic measurements from 1,986 female U.S. Army personnel, meticulously collected by the Natick Soldier Research, Development, and Engineering Center (NSRDEC) as part of the 2012 ANSUR II survey. Anthropometric variables such as stature, waist circumference, chest circumference, and thigh circumference were measured using standardized protocols with high-precision instruments, including stadiometers, calipers, and tape measures. To ensure accuracy and reliability, the data collection process adhered to rigorous methodological standards, minimizing variability and measurement error. Demographic variables, including age, ethnicity, and military component (e.g., Regular Army, Reserve), were cross-referenced with administrative records, further enhancing the validity of the dataset.

Although other publicly available datasets focus on anthropometric measurements, they are typically centered on civilian populations or mixed-gender samples, which do not capture the unique physical demands and requirements of military personnel. Civilian datasets often lack the granularity necessary to account for the operational and performance-based contexts of military service, where precise body measurements can impact everything from uniform design to load-bearing capacity and overall readiness. Moreover, military-specific datasets are rarely accessible to researchers due to stringent security and privacy concerns, creating a significant gap in publicly available data for this specialized group.

The ANSUR II dataset bridges this gap by providing one of the most comprehensive sources of anthropometric and demographic data specific to female military personnel. This specificity is crucial for understanding the physical characteristics and needs of female soldiers, who face unique challenges compared to their male counterparts. The dataset's depth allows researchers to analyze relationships between body dimensions and factors such as physical performance, injury risk, and operational readiness. Furthermore, it offers valuable insights for developing tailored fitness programs, improving gear design, and enhancing overall health and safety standards in military contexts.

Given its rarity and specificity, the ANSUR II dataset is an invaluable resource for researchers and policymakers interested in advancing the well-being and effectiveness of female U.S. Army personnel. By enabling analyses that would otherwise be impossible with civilian datasets, it contributes to a deeper understanding of the unique anthropometric and demographic characteristics of this population, paving the way for evidence-based interventions and policy decisions.

@@

The `tidyverse` package [@tidyverse] was used to streamline the entire process of data manipulation, transformation, and visualization, ensuring consistency, efficiency, and flexibility throughout the analysis. Its comprehensive suite of tools enabled the creation of tailored and informative visual outputs, as well as the effective transformation and summarization of complex datasets.

The implementation of Bayesian models was facilitated by `rstanarm` [@rstanarm], which provided a straightforward way to fit regression models using Stan. Diagnostic and posterior predictive checks were conducted using `bayesplot` [@bayesplot], allowing for thorough assessment of model fit through graphical outputs. The `arrow` package [@arrow] enhanced data handling by enabling efficient reading and writing of large datasets.

To present data and model outputs effectively, `tinytable` [@tinytable] was used to create compact and well-organized summary tables, while `modelsummary` [@modelsummary] provided professional-quality regression tables and visualizations, ensuring clarity in summarizing model results. Dynamic and reproducible reporting was achieved with `knitr` [@knitr], integrating R code with outputs for seamless inclusion of plots and analysis in the final document. For data cleaning, `janitor` [@janitor] was instrumental in preprocessing dirty data into a clean, analysis-ready format.

Finally, the book Telling Stories with Data [@tellingstories] was consulted as a statistical reference, providing valuable insights to support the analysis and visualization strategies employed in this study.

@@

### Body Weight in Pounds

@@

ggplot(data = analysis_data, aes(x = weightlbs)) +
  geom_histogram(binwidth = 2, fill = "steelblue", color = "grey50") +
  labs(
    x = "Body Weight (lbs)",
    y = "Count"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))
```

@@

### Height

@@

ggplot(data = analysis_data, aes(x = heightin)) +
  geom_histogram(binwidth = 2, fill = "darkgreen", color = "grey50") +
  labs(
    x = "Height (inches)",
    y = "Count"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))
```

### Waist Circumference

@@

### Thigh Circumference

@@

# Example dataset (use your cleaned data instead)
data <- analysis_data

@@

# Create violin plots
ggplot(data_long, aes(x = measurement, y = value, fill = measurement)) +
  geom_violin(trim = FALSE, alpha = 0.7) + # Violin plot with full tails
  geom_jitter(width = 0.2, alpha = 0.5, color = "black") + # Overlay actual data points
  theme_minimal() +
  labs(
    x = "Measurement",
    y = "Circumference (in cm)",
    fill = "Measurement"
  ) +
  theme(legend.position = "none")
```

### Age

@@

# Summary statistics for age
age_summary <- analysis_data %>%
  summarise(
    Min = min(age, na.rm = TRUE),
    `1st Quartile` = quantile(age, 0.25, na.rm = TRUE),
    Median = median(age, na.rm = TRUE),
    `3rd Quartile` = quantile(age, 0.75, na.rm = TRUE),
    Max = max(age, na.rm = TRUE),
    Mean = mean(age, na.rm = TRUE),
    SD = sd(age, na.rm = TRUE)
  )

@@

# Display the table
age_table
```

### Component

@@

# Frequency table for component
component_summary <- analysis_data %>%
  count(component) %>%
  mutate(Percentage = round(n / sum(n) * 100, 2))

@@

# Display the table
component_table
```

@@

The model's design reflects the characteristics of the dataset to ensure alignment with the nature of the variables and optimize the analysis. Anthropometric variables such as height, waist circumference, and thigh circumference were included as continuous predictors to preserve their granularity and maximize sensitivity to subtle variations in body weight. Age was also treated as a continuous variable, rather than being grouped into categories, to avoid arbitrary cutoffs and retain variability, enabling a more precise assessment of its relationship with body weight. The military component variable was modeled categorically, with each group (Regular Army, Reserves, and National Guard) treated as a distinct level to account for structural differences in activity levels and lifestyle among these groups. Additionally, waist and thigh circumferences were rescaled to centimeters for consistency and to reflect standard real-world measurement practices. These decisions ensure that the model leverages the dataset's structure effectively while maintaining interpretability and relevance to the research context.

@@

-   Intercept Priors: For the model's intercept $\beta_0$, a normal prior distribution is used with a mean of 0 and a standard deviation of 1. This choice reflects the assumption that the baseline body weight (when all predictors are zero) is centered near the observed scale of the outcome variable but avoids imposing overly strong constraints. The standard deviation of 1 allows for reasonable variation, ensuring the prior does not dominate the posterior estimates. Given the scale of the predictors (e.g., height, waist circumference), this weakly informative prior stabilizes the intercept estimate without introducing bias.

@@

The weakly informative priors are designed to enhance the model's robustness, ensuring credible parameter estimates and reliable uncertainty quantification. The use of Bayesian priors provides an added layer of rigor, particularly when estimating complex relationships between predictors and body weight. The rstanarm package facilitates the implementation of these priors, making Bayesian inference accessible and effective for this analysis.

@@

A frequentist linear regression model was also considered for its simplicity and interpretability; however, it does not provide posterior distributions or credible intervals, which are essential for quantifying uncertainty in this study. By contrast, the Bayesian regression framework provides probabilistic estimates, enabling uncertainty quantification and credible intervals for the coefficients. This approach aligns well with the study's objectives, where understanding the relative influence of predictors on body weight requires a robust and interpretable model. The rstanarm package was chosen for its efficient handling of Bayesian inference and built-in diagnostics, ensuring rigorous validation. The Gaussian likelihood function complements the continuous nature of the outcome variable (body weight), and the model structure strikes a balance between simplicity and capturing key relationships in the data.

@@

The Bayesian regression model was developed to investigate the relationship between body weight and key anthropometric and demographic predictors among female U.S. Army personnel. The predictors included height, waist circumference, thigh circumference, age, and military component. The analysis identified significant positive associations between body weight and the anthropometric predictors---height, waist circumference, and thigh circumference---highlighting their strong influence on body weight. Age and military component demonstrated smaller but meaningful effects, reflecting their nuanced contributions to variations in body weight. A summary of these findings is presented in [@tbl-bayesian-model-summary].

@@

library(rstanarm)
bayesian_model <-
  readRDS(file = here::here("models/bayesian_model.rds"))
```

@@

# Create a summary table using modelsummary
modelsummary(
  list("Bayesian Regression Model" = bayesian_model),
  statistic = c("conf.int", "std.error"), # Include credible intervals and standard errors
  stars = FALSE, # Disable statistical significance stars
  gof_omit = ".*"
)
```

@@

The model's intercept represents the baseline body weight when all predictors are at their reference levels or zero. While this value lacks direct interpretability due to the unrealistic scenario of zero predictors, it provides a conceptual starting point for the model. These findings emphasize the importance of anthropometric measurements in predicting body weight while underscoring the need for further exploration of demographic factors to refine the model.

@@

posterior <- as.matrix(bayesian_model)

mcmc_areas(
  posterior,
  pars = c("heightin", "waist_circumference", "thigh_circumference", "age", "componentArmy Reserve", "componentRegular Army"),
  prob = 0.89, # 89% credible intervals
  prob_outer = 0.95
) +
  ggtitle("Posterior Distributions of Coefficients") +
  xlab("Estimated Effect") +
  theme_classic()
```

@@

The Bayesian regression analysis underscores the significant positive associations between body weight and anthropometric predictors, particularly waist circumference and thigh circumference, among female U.S. Army personnel. These findings highlight the critical role of body composition measurements in explaining variations in body weight. Conversely, the uncertain effects of height, age, and military component suggest that these factors contribute less reliably to the model, reflecting the multifaceted nature of weight determinants. These results affirm the utility of anthropometric data in health monitoring and fitness interventions while identifying areas for further refinement. Exploring additional predictors may enhance the model's explanatory power and improve its utility in practical applications.

@@

This research underscores the utility of anthropometric measurements in predicting body weight, providing actionable insights for health monitoring, fitness interventions, and military equipment design. For instance, the findings could guide the development of tailored fitness programs to address central adiposity (waist circumference) and muscle mass (thigh circumference), enhancing operational readiness and reducing injury risks. These insights align with broader public health objectives, such as the World Health Organization's emphasis on preventing obesity-related conditions through effective weight management strategies.

@@

Expanding the dataset's scope to include longitudinal measurements would also enable researchers to explore dynamic relationships between body composition, fitness, and operational readiness. Such studies could inform policies for optimizing physical performance and reducing long-term health risks among service members.

@@

The raw ANSUR II Female Dataset was systematically cleaned and prepared for analysis to ensure consistency, accuracy, and relevance of the variables. First, the raw dataset was loaded using the read_csv function and processed with the janitor::clean_names() function to standardize column names, making them easier to interpret and work with. Key variables relevant to the study---such as weight (weightlbs), height (heightin), waist circumference, thigh circumference, age, and military component---were selected using the select() function to focus the analysis on predictors of interest.

@@

[@fig-ppcheckandposteriorvsprior-1] presents a posterior predictive check to evaluate how well the model predicts the observed data. This diagnostic compares the simulated data from the model's posterior distribution with the actual observed data, providing insights into the model's adequacy. A good fit is characterized by overlapping distributions of predicted and observed values, indicating that the model effectively captures key characteristics of the data.

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: Examining how the model fits, and is influenced by the data.
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
pp_check(bayesian_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(bayesian_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

[@fig-stanareyouokay-1] presents a trace plot, which assesses the convergence of the Markov Chain Monte Carlo (MCMC) algorithm by examining the sampled values for each parameter across iterations. The chains for each parameter exhibit good mixing, with no discernible trends or patterns over the iterations. The consistent overlap of chains indicates that the sampling algorithm has effectively explored the posterior distribution. These results suggest that the Bayesian model's estimates are reliable and not overly sensitive to initial values or random sampling variation.

@@

plot(bayesian_model, "trace")
plot(bayesian_model, "rhat")
```

@@

## Budget Allocation

To implement the survey effectively, a budget of \$60,000 has been allocated across key components. Recruitment efforts are estimated to cost \$10,000, including expenses for email campaigns, newsletters, physical flyers, and outreach via social media platforms. Incentives, such as gift cards or community recognition, are also included to encourage participation. Data collection accounts for \$25,000, covering the training of professionals, purchasing and calibrating measurement equipment, licensing survey platforms, and logistics for in-person survey administration. Statistical sampling and quality control measures, such as stratified random sampling, cross-verification, and pilot testing, are allocated \$15,000. Finally, \$10,000 is designated for data analysis and report preparation, ensuring comprehensive reporting and stakeholder communication.

## Recruitment Strategy

A multi-channel approach will be employed to recruit participants and ensure representation across all military components. Direct outreach through internal military communication systems, including email campaigns, newsletters, and base announcements, will be complemented by online recruitment via social media groups and forums frequented by U.S. Army personnel. In-person recruitment efforts, such as hosting information sessions and setting up booths at military installations, will further support participant engagement. To maximize response rates, incentives like gift cards or recognition within the military community will be offered.

## Sampling Method

The study will utilize a stratified random sampling approach to ensure the sample accurately reflects the diverse population of female U.S. Army personnel. Strata will be defined based on military component (Active Duty, Reserves, National Guard), age groups (18–25, 26–35, 36+ years), and ethnic backgrounds. Participants will be randomly selected within each stratum using computer-generated random numbers, with proportional allocation to mirror population distribution. To ensure adequate representation of smaller groups, such as Reserve personnel or minority ethnic groups, oversampling will be applied, doubling the sample size in these strata to address potential non-response challenges.

## Data Collection Process

Anthropometric measurements, including weight, height, waist circumference, and thigh circumference, will be conducted by trained professionals using calibrated instruments to ensure precision and reliability. Demographic data, such as age, ethnicity, and military component, will be collected via self-reported survey responses and cross-verified with administrative records. Surveys will be administered online using secure platforms like Qualtrics or SurveyMonkey, while in-person administration at military facilities will provide accessibility for personnel without internet access. This dual-mode approach ensures flexibility and inclusivity in data collection.

## Quality Control and Validation

To ensure data accuracy and reliability, several quality control measures will be implemented. Responses will be cross-verified with military records to validate demographic information. Pilot testing will be conducted with a small, diverse sample to refine survey questions and address logistical challenges. Response quality will be assessed by reviewing response times and identifying duplicates using IP tracking for online submissions. Measurement validation protocols, including regular calibration of equipment and standardization of procedures, will minimize variability. Ethical compliance will be ensured through Institutional Review Board (IRB) approval, and data privacy will be safeguarded through anonymization and encryption.

This comprehensive methodology ensures robust, accurate, and representative data collection while addressing practical, ethical, and logistical considerations. By employing stratified random sampling, rigorous data validation, and inclusive recruitment strategies, the study is well-positioned to deliver valuable insights into the determinants of body weight among female U.S. Army personnel.

@@

### Section 1: Demographic Information

1.  **What is your age?** (Open-ended)\
    Example answer: 25

2.  **Which military component are you currently serving in?** (Multiple-choice)

    -   Regular Army\
    -   Army Reserve\
    -   National Guard

3.  **What is your ethnic background?** (Multiple-choice)

    -   White\
    -   Black or African American\
    -   Asian\
    -   Hispanic or Latino\
    -   Native American or Alaska Native\
    -   Native Hawaiian or Pacific Islander\
    -   Other (please specify): \_\_\_\_\_\_\_\_\_\_\_

### Section 2: Anthropometric Measurements

*(Instructions: Please provide accurate measurements. Measurements should be taken by a trained professional or using calibrated equipment.)*

4.  **What is your body weight in pounds?** (Open-ended)\
    Example answer: 142

5.  **What is your height in inches?** (Open-ended)\
    Example answer: 64

6.  **What is your waist circumference in centimeters?** (Open-ended)\
    Example answer: 85.0

7.  **What is your thigh circumference in centimeters?** (Open-ended)\
    Example answer: 62.2

### Section 3: Additional Information
